---
title: "FInal Project"
author: "Hanna Mogensen & Chloe Pearson"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Map (otalith, tagging sites, receivers sites, water sites)

```{r setup, include=FALSE}

```

# Map (density of detections by receiver)
  Hanna is going to work on finding a basemap of Great Bay
  Chloe is going to work on getting lats and longs for each point

# 2 Animations (paths of two different individual smelt)
1st Priority: 
  53786 - Bellamy river, M
  53774 - Squamscott river, F

2nd Priority:
  53792 - Squamscott river, M
  53801 - Oyster river, M
  
# 2 Figures of Data (fish characteristics)
  Otolith vs. tag by length and sex (by river?)
  Otolith by date?? add image as background? 
  



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
